Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-07-22 replication_paper/pnas_draft/paper.Rmd
01-04 reproduce

ft_cuba_precision %>% save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_precision.png", zoom=1) # webshot = "webshot2"
temp <- NULL

@@

\clearpage
\onecolumn
\begin{figure}[H]
\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=22cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_precision.png"}}
\end{figure}
\clearpage
\twocolumn

@@

#Replace emoticons with images
replace_emoticons <- function(x){
  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q241.png) ") %>%
        #https://emojiterra.com/flag-for-united-states/
        str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
        #https://emojiterra.com/flag-for-russia/
        str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15180.png) ") %>% 
        #Turkey
        str_replace_all('\U0001f1f9\U0001f1f7',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q43.png) ") %>% 
        #U.N.
        str_replace_all('\U0001f1fa\U0001f1f3',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q1065.png) ")
}

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_cuban_recall.png", zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

#Replace emoticons with images
replace_emoticons_crimea <- function(x){
      x %>%
            #https://emojiterra.com/flag-for-united-states/
            str_replace_all('\U0001f1fa\U0001f1f8',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q30.png) ") %>%
            #https://emojiterra.com/flag-for-russia/
            str_replace_all('\U0001f1f7\U0001f1fa',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q159.png) ") %>% 
            #Ukraine
            str_replace_all('\U0001f1fA\U0001f1e6',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q212.png) ") %>% 
            #
            str_replace_all('Crimea',  " ![](/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small//Q15966495.png) ")
}

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/case_study_crimea_recall.png",
                  zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea.png", zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

library(magick)
tiger <- image_read("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea.png")
tiger2 <- image_read(paste0(here::here(), '/replication_paper/figures/p_recall.png'))

combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
image_write(combined, "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea_andcounts.png")

@@

\clearpage
\onecolumn
\begin{figure}[H]
\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
\centering{\includegraphics[height=18cm]{/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/recall_cuban_and_crimea_andcounts.png}}
\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents. Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
\end{figure}
\clearpage
\twocolumn

@@

icews_clean_subset_top10_day <- read_tsv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/data/out/icews_clean_471_lowest.tsv")

>>>>

ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","pnas_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
temp <- NULL

@@

\clearpage
\onecolumn
\begin{figure}[H]
\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=22cm]{"./case_study_cuban_precision.png"}}
\end{figure}
\clearpage
\twocolumn

@@

paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")

#Replace emoticons with images
replace_emoticons <- function(x){
  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
        #https://emojiterra.com/flag-for-united-states/
        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
        #https://emojiterra.com/flag-for-russia/
        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
        #Turkey
        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
        #U.N.
        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
}

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

#Replace emoticons with images
replace_emoticons_crimea <- function(x){
      x %>%
            #https://emojiterra.com/flag-for-united-states/
            str_replace_all('\U0001f1fa\U0001f1f8', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
            #https://emojiterra.com/flag-for-russia/
            str_replace_all('\U0001f1f7\U0001f1fa', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q159.png) ")) %>% 
            #Ukraine
            str_replace_all('\U0001f1fA\U0001f1e6',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q212.png) ")) %>% 
            #
            str_replace_all('Crimea', paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15966495.png) "))
                            }

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_recall.png"),
                  zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

library(magick)

tiger <- image_read(here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea.png"))
tiger2 <- image_read(paste0(here::here(), '/replication_paper/figures/p_recall.png'))

combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
image_write(combined, here::here("replication_paper", "pnas_draft", "recall_cuban_and_crimea_andcounts.png"))

@@

\clearpage
\onecolumn
\begin{figure}[H]
\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
\centering{\includegraphics[height=18cm]{/recall_cuban_and_crimea_andcounts.png}}
\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents. Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
\end{figure}
\clearpage
\twocolumn

@@

icews_clean_subset_top10_day <- read_tsv(here::here("replication_paper", "data", "out", "icews_clean_471_lowest.tsv"))
